# Page 3


#### 6. Add legend to the heatmap. (5 pts)
Based on the figure from 5, put color bars on both row side and column side to denote species. add appropriate legend at appropriate location.

```{r  fig.width=5, fig.height=5}
Species <- iris$Species
color0 <- Species
levels(color0) <- c("red","green","blue")
heatmap.2(cor_df, Rowv = FALSE, Colv = FALSE, scale = "none", dendrogram = "none", trace = "none", RowSideColors = as.character(color0), ColSideColors = as.character(color0))

legend("topright",legend = levels(Species),fill = levels(color0))
```

#### 7.Scattered plot. (5 pts)
Draw scattered plot of Sepal.Length (x axis) versus Sepal.Width (y axis).
Color the dots with the following coding (setosa: red. versicolor: green; virginica: blue).
You can use any function, but **there should be no figure legend for this question**.

```{r}
## your code
c_scheme <- ifelse(iris$Species == "setosa","red",ifelse(iris$Species =="versicolor","green","blue"))



plot(iris$Sepal.Length, iris$Sepal.Width, xlab = "Sepal Length", ylab = "Sepal Width", col = c_scheme,  pch = 16)

```

#### 8. Add legend. (5 pts)
Based on the figure from 7, add appropriate legend (for species) at appropriate location.
In the legend, you should have the same type of dot symbol (color and shape as the dots in the figure) as well as species names. 
You can use any function. 

```{r}
## your code

Species <- iris$Species
color0 <- Species
levels(color0) <- c("red","green","blue")

plot(iris$Sepal.Length, iris$Sepal.Width, xlab = "Sepal Length", ylab = "Sepal Width", col = c_scheme, bg = c_scheme, pch = 16)

legend("topright",legend = levels(Species),col = levels(color0), pch = 16)

```

#### 9. Add regression lines. (5 pts)
Based on the previous figure, add regression lines on top of the scattered plot for each species.
The line color should be consistent with dots colors.
If you need more hints refer to here <http://www.statmethods.net/graphs/scatterplot.html> (use abline() function).
Note that in this question you don't have to draw a legend.
Again, you can also use function (you don't have to use the hint). 

```{r}
## your code


plot(iris$Sepal.Length, iris$Sepal.Width, xlab = "Sepal Length", ylab = "Sepal Width", col = c_scheme, bg = c_scheme, pch = 16)

abline(lm(Sepal.Width~Sepal.Length,data = iris, subset = Species == "setosa"), col = "red")
abline(lm(Sepal.Width~Sepal.Length,data = iris, subset = Species == "versicolor"), col = "green")
abline(lm(Sepal.Width~Sepal.Length,data = iris, subset = Species == "virginica"), col = "blue")

```

